### 2021-09-09 input/abstract.tex
address Adrien's comments

  %%% Our proposal
  \noindent In this paper, we abstract content indexing as distributed
  partitioning:
  every \process only indexes its closest replica, and
  connected \processes with a similar index compose a partition. Our
  decentralized implementation \NAME is
  \begin{inparaenum}[(i)]
  \item efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time. As
  such, \NAME can constitute a new building block for geo-distributed
  services.
\end{abstract}

>>>>

  %%% Our proposal
  \noindent In this paper, we abstract the content indexing challenge
  as a distributed partitioning problem: every \process only indexes
  its closest replica, and connected \processes with a similar index
  compose a partition. Our decentralized implementation \NAME is
  \begin{inparaenum}[(i)]
  \item efficient, for it uses partitions to lock down the traffic
    generated by its operations to relevant \processes, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time.
  %% As
  %% such, \NAME can constitute a new building block for geo-distributed
  %% services.
\end{abstract}

### 2021-09-09 input/conclusion.tex
integrate CDN but not satisfying
address Adrien's comments

As future work, we plan to enable lazy retrieval of partitions when a
large number of \TODO{objects} is involved. Indeed, using \NAME, every
\process partakes in the propagation of all indexes which raises
scalability issues. We would like to leverage the hierarchical
properties of
% interconnected
autonomous systems to limit the
propagation of such indexes only to interested systems.

>>>>

As future work, we plan to leverage the hierarchical properties of
interconnected autonomous systems to further limit the propagation of
indexes within interested systems only. Systems hosting a large number
of contents would greatly benefit from this improvement.

%% As future work, we plan to enable lazy retrieval of partitions when a
%% large number of contents is involved. Indeed, using \NAME, every
%% \process partakes in the propagation of all indexes which raises
%% scalability issues. We would like to leverage the hierarchical
%% properties of
%% % interconnected
%% autonomous systems to limit the
%% propagation of such indexes only to interested systems.

### 2021-09-09 input/figdel.tex
cosmetic + number
ongoing wip
address Adrien's comments

\begin{figure}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}\Process~$a$ deletes its
      partition.  It notifies all \processes that belong to its
      partition using \NAMEB.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    %
    \subfloat[Part B][\label{fig:delB}$\delta$s stop as soon as they
      encounter another partition. \Process~$b$ answers with its
      partition.]{\input{input/figdelB.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    \NAMEB. \Process~$a$ eventually knows that it belong to Partition
    $P_d$.}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}\Process~$a$ deletes its
      partition.  It notifies all \processes that belong to its
      partition.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    %
    \subfloat[Part B][\label{fig:delB}$\delta$ stops as soon as they
      encounter another partition. \Process~$b$ answers with its
      partition.]{\input{input/figdelB.tex}}
  \end{center}
  \caption{\label{fig:del}Efficient removal of a partition using
    \NAMEB. $a$ eventually knows that it belongs to $P_d$.}
\end{figure}

### 2021-09-09 input/introduction.tex
address Adrien's comments

In recent years, the data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier, foggy_cache, shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,
  confais2017performance, fogstore, hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT)~\cite{maymounkov2002kademlia} spread across
the different \processes composing the infrastructure. When a client
wants to access specific content, it requests a remote \process to
provide at least one \process identity to retrieve this content
from. After it retrieved the content, the client can create another
replica to improve the performance of future accesses, but it must
contact the content indexing service again to notify of such a change.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

These approaches are in contradiction with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays~\cite{asrese2019measuring, doan2019tracing} that
occur even before the actual download started.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer. In turn, clients either waste
network resources, or face lower response time.
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

@@

\noindent The contribution of this paper is threefold:

@@

\item [$\bullet$] We evaluate \NAME with simulations. Our experiments
  empirically support our complexity analysis and the scalability of
  \NAME. Using scoped broadcast, \NAME quickly disseminate messages to
  a subset of relevant \processes. The higher the number of
  partitions, the smaller \NAME's overhead.  Most importantly, \NAME
  does not generate traffic in quiescent systems.  Our experiments
  also highlight the relevance of \NAME in autonomous systems. \NAME
  would allow to lock down the traffic generated by content indexing,
  even in contexts where \emph{physical} partitioning may occur.
  As such, \NAME can constitute a new building block for geo-distributed
  services.
\end{asparadesc}

>>>>

In recent years, the data storage paradigm shifted from centralized in
the cloud to distributed at the edges of the network. 
% There is an ongoing evolution of storing data from the cloud to the
% edges of the network.
This change aims at keeping the data close to
\begin{inparaenum}[(i)]
\item its producers since data may be too expensive or sensitive to be
  transmitted through the network; and
\item its consumers so data may quickly and efficiently reach
  them~\cite{cachier, foggy_cache, shi2016edge}.
\end{inparaenum}
%% It avoids transmitting Either because it is where it has been
%% created and it is too expensive to be transmitted through the
%% network, or because it has been replicated to bring data closer to
%% the end users ~\cite{shi2016edge, foggy_cache, cachier}.
%
To favour this transition, new designs for data management across Edge
infrastructures have been investigated~\cite{confais2017object,
  confais2017performance, fogstore, hasenburg2020towards}.  They
enable strategies to confine traffic by writing data locally and
replicating content according to effective needs. However, locating
content remains challenging. Retrieving a content location may
actually take more time than retrieving the content itself.
%% Although
%% these systems, provide good properties such as favouring network
%% traffic confinement by writting data locally and replicating contents
%% according to the effective needs, determining the location where to
%% get the content might be more expensive than retrieving the content
%% itself.
%
Indeed, these systems, when not using a centralized index hosted in a
Cloud, rely on \underline{d}istributed \underline{h}ash
\underline{t}ables (DHT) spread across the different \processes
composing the infrastructure~\cite{maymounkov2002kademlia}. When a
client wants to access specific content, it requests a remote \process
to provide at least one \process identity to retrieve this content
from. After it retrieved the content, the client can create another
replica to improve the performance of future accesses, but it must
contact the indexing service again to notify of the creation of this
new replica.
%% a local replica is created to improve the performance for future
%% accesses and the process in charge of maintaining the index is
%% contacted once again to reflect this new location.
%

@@

Such approaches are in contradiction with the objectives of Edge
infrastructures that aim at reducing the impact of latency as well as
the volume of data passing through the network.
%
First, accessing a remote \node to request content location(s) raises
hot spots and availability issues. But most importantly, it results in
additional delays~\cite{asrese2019measuring, doan2019tracing} that
occur even before the actual download started.
%
Second, the client gets a list of content locations at the discretion
of content indexing services. Without information about these
locations, it often ends up downloading from multiple replica hosts,
yet only keeping the fastest answer. In turn, clients either waste
network resources, or face lower response time.
%% there is no information to select the ``best'' node among the
%% possible candidates from which the content could be retrieved. In
%% most cases, this results in parallel requests performed by the
%% client node to each candidate with the goal of retrieving the
%% content as efficient as possible.

@@

\noindent In this paper, we address these issues and limitations
regarding content indexing. Our contribution is threefold:

@@

\item [$\bullet$] We evaluate \NAME with simulations. Our experiments
  empirically support our complexity analysis and the scalability of
  \NAME. Using scoped broadcast, \NAME quickly disseminate messages to
  a subset of relevant \processes. The higher the number of
  partitions, the smaller \NAME's overhead.  Most importantly, \NAME
  does not generate traffic in quiescent systems.  % Our experiments
  %  also highlight the relevance of \NAME in autonomous systems.
  \NAME would allow to lock down the traffic generated by content
  indexing, even in contexts where \emph{physical} partitioning may
  occur.
  %As such, \NAME can constitute a new building block for
  % geo-distributed services.
\end{asparadesc}

### 2021-09-09 input/proposal.tex
address Adrien's comments

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issues with
dynamic partitions, even in contexts where \processes have FIFO links,
\ie where \processes receive the messages in the order of their
sending ($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
r_q(m')$). Both $a$ and $d$ add then delete their partition
concurrently. \Process~$c$ receives, delivers, and forwards
$\alpha_d^3$ followed by $\delta_d$. In the meantime, $b$ receives,
delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
both $c$ and $d$ deliver the message about Partition $P_a$, for they
did not have any known partition at receipt time. On the contrary, $b$
delivers $\alpha_d^1$, for it improves its distance to a known
source. \Process~$b$ then blocks $a$'s removal notification
$\delta_a$. It never reaches $c$ nor $d$. Also, $c$ does not deliver
$\alpha_d$ and $\delta_d$ since it already delivered it. The system
converges to an inconsistent state where some \processes assume they
belong to a partition while it does not exist anymore.

@@

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$). \Processes never reach
    consistent partitioning.
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, the \process never
    ends up in its best partition. Therefore, \processes do not reach
    consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process ($S(\alpha_a) \implies
    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
    removal eventually triggers the forwarding of best delivered
    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
    \processes may deliver other stale messages that will be 
    eventually removed to never be delivered again. In the worst case,
    all \processes deliver and remove all stale messages to ultimately
    deliver and forward only up-to-date messages ($\eventually d_c(m')
    \implies \neg S(m')$). As in Theorem~\ref{theo:bef}, they
    eventually deliver and forward their best up-to-date message.

@@

\begin{proof}
  We must prove that every \process that delivered a stale $\alpha_X$
  eventually
  \begin{inparaenum}[(i)]
  \item delivers a better $\alpha_Y$, or 
  \item delivers a removal notification of $\alpha_X$.
  \end{inparaenum}
  Figure~\ref{fig:proofB} summarizes the issue of purging in scenarios
  involving concurrent operations:

  If every \process (such as $a$) starting from the source delivers
  and forwards a removal notification $\delta_X$ when their last
  delivery is $\alpha_X$, then every such \process eventually delivers
  the removal notification $\delta_X$ except \processes (such as $b$)
  that delivered $\alpha_X$ from a \process that delivered a message
  from another partition $\alpha_Y$ since then.

@@

  Assuming that every \process keeps an history of its past
  deliveries, \processes (such as $c$) can detect the inconsistency,
  since they receive from their parent an already deleted partition
  $P_Y$. This notification means that the parent discards any
  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
  $\delta_X$ exists, it discards it. To ensure the purge of stale
  messages, a detecting \process must assume the worst case that such
  $\delta_X$ exists, and send another kind of message, noted $\Delta$,
  that notify the possible removal of $P_X$.

  A \process (such as $d$) whose last delivery is $\alpha_X$, but
  whose parent is neither inconsistent (like $b$) nor receiving

>>>>

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issues with
dynamic partitions, even in contexts where \processes have FIFO links,
\ie where \processes receive the messages in the order of their
sending ($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
r_q(m')$). Both $a$ and $d$ add then delete their partition
concurrently. \Process~$c$ receives, delivers, and forwards
$\alpha_d^3$ followed by $\delta_d$. In the meantime, $b$ receives,
delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
both $c$ and $d$ deliver the message about Partition $P_a$, for they
did not have any known partition at receipt time. On the contrary, $b$
delivers $\alpha_d^1$, for it improves its distance to a known
source. \Process~$b$ then blocks $a$'s removal notification
$\delta_a$. It never reaches $c$ nor $d$. Also, $c$ does not deliver
$\alpha_d$ and $\delta_d$ since it already delivered it. The system
converges to an inconsistent state where some \processes assume they
belong to a partition while it does not exist anymore. The system
needs to purge stale $\alpha$ messages that stop $\delta$ messages
from reaching nodes.
%The system needs to
% purge its stale messages.

@@

\begin{proof}
  %% To reach consistent partitioning, the last message delivered by
  %% every process is not stale and comes from its respective best
  %% source: $d(m)$
  Assuming EFB as default propagation behavior where \processes
  deliver and forward the best sum of weights they received. We must
  prove that despite stale messages, the last delivery of every
  \process is the message that followed the shortest path to its
  closest source.
  \begin{asparadesc}
  \item [EFB without Purge:] From Figure~\ref{fig:problemD}, a
    \process may receive messages in such an order ($d_b(\alpha_d^1)
    \rightarrow r_b(\delta_a) \rightarrow d_b(\delta_d)$) that it does
    not forward messages required by other \processes
    ($\delta_a$). The last delivery of some nodes ($c$ and $d$) is
    wrong ($\alpha_a^3$ instead of $\delta_a$).
    % \Processes never
    % reach consistent partitioning.
    %
    %% Figure~\ref{fig:proofA} depicts the generic case where a \process
    %% $b$ precludes itself and subsequent \processes such as $c$ of
    %% delivering the message from their respective best source
    %% $a$. \Process $b$ received and delivered a message from a
    %% partition that has since then been deleted but with a better sum
    %% of weights than newly received ones ($\alpha_d^y <
    %% \alpha_a^{x'}$). It forever discards such a message
    %% $\alpha_a^{x'}$.
  \item [Purge not followed by EFB:]
    %% also transiting messages
    Assuming that every \process removes control information as soon
    as it becomes stale ($S(\alpha_a) \implies d_b(\alpha_a^x)
    \rightarrow d_b(\delta_a)$) and cannot deliver stale messages
    anymore ($S(\alpha_a^x) \implies d_c(m) \rightarrow \ldots
    \rightarrow d_c(m' \not\in \alpha_a)$), staleness does not impair
    up-to-date messages propagation. However, even in such settings,
    depending on receipt order ($d_b(\alpha_a^{x}) \rightarrow
    r_b(\alpha_c^{y : y > x}) \rightarrow d_b(\delta_b)$), a \process
    may never receive again, hence deliver and forward a message that
    was received and discarded before ($\alpha_c^{y}$). When such a
    message contains its best up-to-date partition, a \process may
    never end up in its best partition.
    %    Therefore, \processes do not reach
    % consistent partitioning.
  \item [Purge then EFB:] Assuming the eventual and definitive removal
    of stale messages at each \process ($S(\alpha_a) \implies
    (d_b(\alpha_a) \implies \eventually d_b(\alpha_a) \rightarrow
    d_b(m') \not\rightarrow d_b(\alpha_a))$); and assuming that every
    removal eventually triggers the forwarding of best delivered
    messages ($d_c(\delta_x) \implies \eventually f_d(\alpha_y)$),
    \processes may deliver other stale messages that will be 
    eventually removed to never be delivered again. In the worst case,
    all \processes deliver and remove all stale messages to ultimately
    deliver and forward only up-to-date messages ($\eventually d_c(m')
    \implies \neg S(m')$). As in Theorem~\ref{theo:bef}, they
    eventually deliver and forward their best up-to-date message.

@@

\begin{proof}
  We must prove that every \process that delivered a stale $\alpha_X$
  eventually delivers a better $\alpha_Y$, or delivers a removal
  notification of $\alpha_X$.  Figure~\ref{fig:proofB} summarizes the
  issue of purging in scenarios involving concurrent operations.

  (i) If every \process (such as $a$) starting from the source
  delivers and forwards a removal notification $\delta_X$ when their
  last delivery is $\alpha_X$, then every such \process eventually
  delivers the removal notification $\delta_X$ except \processes (such
  as $b$) that delivered $\alpha_X$ from a \process that delivered a
  message from another partition $\alpha_Y$ since then.

@@

  (ii) Assuming that every \process keeps an history of its past
  deliveries, \processes (such as $c$) can detect the inconsistency,
  since they receive from their parent an already deleted partition
  $P_Y$. This notification means that the parent discards any
  $\delta_Z$ with $\alpha_Z^z < \alpha_Y^y$, and most importantly, if
  $\delta_X$ exists, it discards it. To ensure the purge of stale
  messages, a detecting \process must assume the worst case that such
  $\delta_X$ exists, and send another kind of message, noted $\Delta$,
  that notify the possible removal of $P_X$.

  (iii) A \process (such as $d$) whose last delivery is $\alpha_X$,
  but whose parent is neither inconsistent (like $b$) nor receiving
